A Study on Common Bug Fix Patterns in Rust

### 2022-09-20 main.tex
fix compilation errors
reorganized files

\documentclass{article}
\usepackage{listings, listings-rust}
\lstset{escapeinside={<@}{@>}}
\usepackage{minted}
\usepackage{tabularx}
\usepackage{array}
\usepackage{graphicx}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage[utf8]{inputenc}
\usepackage{multirow}
\usepackage{subfiles} % Best loaded last in the preamble

\title{Rust Bug Fix Patterns}
\author{Moh Robati}

\begin{document}
\maketitle

\section{Introduction}
\subfile{1_introduction}

\section{Methodology}
\subfile{2_methodology}

\section{Results}
\subfile{3_results}

\section{Discussion}
\subfile{4_discussion}

\section{Conclusion}
\subfile{5_conclusion}

\end{document}

>>>>

%%%%%%%%%%%%%%%%%%%%%%% file template.tex %%%%%%%%%%%%%%%%%%%%%%%%%
%
% This is a general template file for the LaTeX package SVJour3
% for Springer journals.          Springer Heidelberg 2010/09/16
%
% Copy it to a new file with a new name and use it as the basis
% for your article. Delete % signs as needed.
%
% This template includes a few options for different layouts and
% content for various journals. Please consult a previous issue of
% your journal as needed.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% First comes an example EPS file -- just ignore it and
% proceed on the \documentclass line
% your LaTeX will extract the file if required
\begin{filecontents*}{example.eps}
%!PS-Adobe-3.0 EPSF-3.0
%%BoundingBox: 19 19 221 221
%%CreationDate: Mon Sep 29 1997
%%Creator: programmed by hand (JK)
%%EndComments
gsave
newpath
  20 20 moveto
  20 220 lineto
  220 220 lineto
  220 20 lineto
closepath
2 setlinewidth
gsave
  .4 setgray fill
grestore
stroke
grestore
\end{filecontents*}
%
\RequirePackage{fix-cm}
%
%\documentclass{svjour3}                     % onecolumn (standard format)
%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
\documentclass[smallextended]{build/svjour3}       % onecolumn (second format)
%\documentclass[twocolumn]{svjour3}          % twocolumn
%
\smartqed  % flush right qed marks, e.g. at end of proof
%
\usepackage{graphicx}
%
% \usepackage{mathptmx}      % use Times fonts if available on your TeX system
%
% insert here the call for the packages your document requires
%\usepackage{latexsym}
% etc.
%
% please place your own definitions here and don't use \def but
% \newcommand{}{}
%
% Insert the name of "your journal" with
% \journalname{myjournal}
%

\usepackage{listings, build/listings-rust}
\lstset{escapeinside={<@}{@>}}
\usepackage{hyperref}
\usepackage{tabularx}
\usepackage{array}
\usepackage{graphicx}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage[utf8]{inputenc}
\usepackage{multirow}
\usepackage{subfiles} % Best loaded last in the preamble

\begin{document}

\title{A Study on Common Bug Fix Patterns in Rust%\thanks{Grants or other notes
%about the article that should go on the front page should be
%placed here. General acknowledgments should be placed at the end of the article.}
}
\subtitle{}

%\titlerunning{Short form of title}        % if too long for running head

\author{Mohammad Robati Shirzad         \and
        Patrick Lam %etc.
}

%\authorrunning{Short form of author list} % if too long for running head

\institute{F. Author \at
              first address \\
              Tel.: +123-45-678910\\
              Fax: +123-45-678910\\
              \email{fauthor@example.com}           %  \\
%             \emph{Present address:} of F. Author  %  if needed
           \and
           S. Author \at
              second address
}

\date{Received: date / Accepted: date}
% The correct dates will be entered by the editor

\maketitle

\begin{abstract}
Insert your abstract here. Include keywords, PACS and mathematical
subject classification numbers as needed.
\keywords{First keyword \and Second keyword \and More}
% \PACS{PACS code1 \and PACS code2 \and more}
\subclass{MSC code1 \and MSC code2 \and more}
\end{abstract}

\section{Introduction}
\subfile{sections/introduction}

\section{Methodology}
\subfile{sections/methodology}

\section{Results}
\subfile{sections/results}

\section{Discussion}
\subfile{sections/discussion}

\section{Conclusion}
\subfile{sections/conclusion}

%\begin{acknowledgements}
%If you'd like to thank anyone, place your comments here
%and remove the percent signs.
%\end{acknowledgements}

% Authors must disclose all relationships or interests that 
% could have direct or potential influence or impart bias on 
% the work: 
%
% \section*{Conflict of interest}
%
% The authors declare that they have no conflict of interest.

% BibTeX users please use one of
%\bibliographystyle{spbasic}      % basic style, author-year citations
%\bibliographystyle{spmpsci}      % mathematics and physical sciences
%\bibliographystyle{spphys}       % APS-like style for physics
%\bibliography{}   % name your BibTeX data base

% Non-BibTeX users please use
\begin{thebibliography}{}
%
% and use \bibitem to create references. Consult the Instructions
% for authors for reference list style.
%
\bibitem{RefJ}
% Format for Journal Reference
Author, Article title, Journal, Volume, page numbers (year)
% Format for books
\bibitem{RefB}
Author, Book title, page numbers. Publisher, place (year)
% etc
\end{thebibliography}

\end{document}
% end of file template.tex

### 2022-09-20 sections/results.tex
reorganized files

To give an example, in starship/starship after one of the commits \footnote{\url{https://github.com/starship/starship/commit/56d475578ea508631275772127f49a6949fea6b0}{git_branches.rs}}, the developer borrows the value of $repo\_dir$ to keep the ownership of the object in the current scope. Now this object can then be used in another function invocation ($remove\_dir\_all(repo\_dir)$) which fixes a bug. \\

@@

\begin{lstlisting}[language=Rust, style=colouredRust, label={l3}]
pub fn expand_delimited_square(
--  children: &Vec<TokenNode>,
++  children: &[TokenNode],
) -> Result<hir::Expression, ParseError> {
    // body
}
\end{lstlisting}
\noindent \textbf{Description:} In struct field definition or the types of the function formal parameters, type $\&Vec\<T\>$ changes to $\&[T]$. Clippy can detect the opportunity to apply this pattern. The reason is reducing type complication, as slice types in the form of $\&[T]$ or $\&str$ are usually sufficient for most use cases.

@@

\multirow{10}{*}{General}        
& \multirow{2}{*}{Attributes}    & G.attr.struct  & Modifying the attributes of structs                                        \\
                                 &                                & G.attr.struct.field  & Modifying the attributes of struct fields                                  \\\cline{2-3}
                                 & \multirow{2}{*}{Struct}        & G.struct.field  & Adding/Removing a struct field                                      \\
                                 &                                & G.struct.field.pub  & Modifying the access modifiers of struct fields     
                                  \\\cline{2-3}
                                 & Option                         & G.option  & Changing field type T to T$\langle$Option$\rangle$                     \\\cline{2-3}
                                 & \multirow{4}{*}{Types}         & G.type.field  & Changing a struct field type                                        \\
                                 &                                & G.type.generic  & Changing a generic type                                             \\
                                 &                                & G.type.enum.variant  & Change in enum variant value type                                   \\
                                 &                                & G.type.tuple & Changing the type inside a tuple                                         \\\cline{2-3}
                                 & \multirow{1}{*}{Traits}        & G.trait.bound & TraitBound Change                                               \\\cline{1-3}
\multirow{9}{*}{Borrow Checker} &
\multirow{2}{*}{Clone}                                         & BC.clone.ref & Dropping clone and adding borrowing                                                   \\
                                 &                                & BC.clone.drop & Dropping clone   
                                    \\\cline{2-3}
    & \multirow{3}{*}{Ref and Deref} & BC.ref.add  & Adding Borrowing                                                           \\
                                 &                                & BC.ref.drop  & Removing Borrowing                                                         \\
                                 &                                & BC.deref.to\_string  & Modification in dereferencing a string prior to calling to\_string()                                                            \\\cline{2-3}
                                 & \multirow{2}{*}{Mut}           & BC.mut.add  & Adding mutability                                                          \\
                                 &                                & BC.mut.drop  & Dropping mutability                                                        \\\cline{2-3}
                                 & Vector                         & BC.vec.slice  & Changing a Vec reference to Slice                                           \\\cline{2-3}
                                 & \multirow{1}{*}{Lifetime}      
                                                                 & BC.lifetime.static  & Dropping static lifetime    &                        
                                 \hline

>>>>

To give an example, in starship/starship after one of the commits \footnote{\url{https://github.com/starship/starship/commit/56d475578ea508631275772127f49a6949fea6b0}{git\_branches.rs}}, the developer borrows the value of $repo\_dir$ to keep the ownership of the object in the current scope. Now this object can then be used in another function invocation ($remove\_dir\_all(repo\_dir)$) which fixes a bug. \\

@@

\begin{lstlisting}[language=Rust, style=colouredRust, label={l3}]
pub fn expand_delimited_square(
--  children: &Vec<TokenNode>,
++  children: &[TokenNode],
) -> Result<hir::Expression, ParseError> {
    // body
}
\end{lstlisting}
\noindent \textbf{Description:} In struct field definition or the types of the function formal parameters, type \verb+&Vec<T>+ changes to \verb+&[T]+. Clippy can detect the opportunity to apply this pattern. The reason is reducing type complication, as slice types in the form of \verb+&[T]+ or \verb+&str+ are usually sufficient for most use cases.

@@

\multirow{10}{*}{General}        
& \multirow{2}{*}{Attributes}    & G.attr.struct  & Modifying the attributes of structs                                        \\
                                 &                                & G.attr.struct.field  & Modifying the attributes of struct fields                                  \\\cline{2-3}
                                 & \multirow{2}{*}{Struct}        & G.struct.field  & Adding/Removing a struct field                                      \\
                                 &                                & G.struct.field.pub  & Modifying the access modifiers of struct fields     
                                  \\\cline{2-3}
                                 & Option                         & G.option  & Changing field type T to T$\langle$Option$\rangle$                     \\\cline{2-3}
                                 & \multirow{4}{*}{Types}         & G.type.field  & Changing a struct field type                                        \\
                                 &                                & G.type.generic  & Changing a generic type                                             \\
                                 &                                & G.type.enum.variant  & Change in enum variant value type                                   \\
                                 &                                & G.type.tuple & Changing the type inside a tuple                                         \\\cline{2-3}
                                 & \multirow{1}{*}{Traits}        & G.trait.bound & TraitBound Change                                               \\\cline{1-3}
\multirow{9}{*}{Borrow Checker} &
\multirow{2}{*}{Clone}                                         & BC.clone.ref & Dropping clone and adding borrowing                                                   \\
                                 &                                & BC.clone.drop & Dropping clone   
                                    \\\cline{2-3}
    & \multirow{3}{*}{Ref and Deref} & BC.ref.add  & Adding Borrowing                                                           \\
                                 &                                & BC.ref.drop  & Removing Borrowing                                                         \\
                                 &                                & BC.deref.to\_string  & Modification in dereferencing a string prior to calling to\_string()                                                            \\\cline{2-3}
                                 & \multirow{2}{*}{Mut}           & BC.mut.add  & Adding mutability                                                          \\
                                 &                                & BC.mut.drop  & Dropping mutability                                                        \\\cline{2-3}
                                 & Vector                         & BC.vec.slice  & Changing a Vec reference to Slice                                           \\\cline{2-3}
                                 & \multirow{1}{*}{Lifetime}      
                                                                 & BC.lifetime.static  & Dropping static lifetime
